Memory-aware Adaptive Scheduling of Scientific Workflows On Heterogeneous Architectures\\

### 2024-10-09 main.tex
minor

    %%% CONTEXT %%%
    The analysis of massive datasets, originating from fields such as genomics, 
    remote sensing, or biomedical imaging -- to name just a few -- has become ubiquitous in science;
    this often takes the form of workflows, \iec separate software components chained together
    in some kind of complex pipeline~\cite{DBLP:journals/dbsk/LeserHDEGHKKKKK21}.
    These workflows are usually represented as directed acyclic graphs (DAGs).
    The DAG vertices represent the software components (or, more generally, the workflow \emph{tasks}),
    while the edges model I/O dependencies between the tasks~\cite{adhikari2019survey,liuPacitti}.
    Large workflows with resource-intensive tasks can easily exceed the capabilities of a 
    single computer and are therefore executed on a parallel or distributed platform.
    An efficient execution of the workflows on such platforms requires mapping tasks
    to specific processors; to increase utilization by reusing finished processors,
    one also needs a task schedule (\iec a valid execution order that respects the dependencies)
    and possibly also starting times for the tasks.

    %%% MOTIVATION %%%
    Modern computing platforms are often heterogeneous, meaning they feature varying CPU speeds
    and memory sizes. In general, varying memory sizes make it more challenging to compute
    a schedule that respects all memory constraints -- meaning that no task is executed on a 
    processor with less memory than needed for the task. This is, however, very important to
    avoid (possibly expensive) runtime failures and to provide a satisfactory user experience.
    Hence, building on previous related work~\cite{TODO}, we consider a scheduling problem 
    formulation that takes memory sizes as explicit constraints into account. Its objective is
    the very common \emph{makespan}, which acts as proxy for the total execution time of a
    workflow.

    \begin{itemize}
      \item HEFT (see book chapter) is one of the most popular heuristics (cite a review).
      \item However, existing HEFT variations do not take memory sizes into consideration (\skug{check in related work if true!}).
        Note: 2 papers that deal with memory sizes, but model is very different!
      \item Many scheduling strategies assume that task running times provided to them are accurate. This is not really the case
        in practice. Thus, one needs to adapt the schedule when major deviations occur (which is the case in practice).
        List-based schedulers such as HEFT are not designed for adaptation and would compute a completely schedule from scratch.
    \end{itemize}

@@

    For the size-increased workflows, the graph is produced by the WFGen generator, based on a {\em model workflow} and
    the desired number of tasks.
    We used the real-world workflows as models, except for bacass that lead to errors in the generator.
%
    As number of tasks, we use: 200, \numprint{1000}, \numprint{2000}, \numprint{4000}, \numprint{8000}, \numprint{10000},
    \numprint{15000}, \numprint{18000}, \numprint{20000}, \numprint{25000}, \numprint{30000}.
    We divide the workflows into three groups by size: small ones with up to \numprint{8000} tasks, middle
    ones with \numprint{10000} to \numprint{18000} tasks, and big ones with \numprint{20000} to \numprint{30000} tasks.

    \skug{Im still considerin adding category "tiny" with original workflows and those with 200 tasks. this needs to be double-checked after}
    Overall, this yields four workflow types, denoted by tiny, small, mid, and big.

>>>>

    %%% CONTEXT %%%
    \begin{itemize}
      \item What is a scientific workflow?
      \item Scientific workflows are all over the place $\rightarrow$ important!
      \item Scheduling (order, maybe even concrete starting times) is important for efficient workflow executions
      \item Only mapping tasks to processors is not enough.
      \item This also allows to reuse processors, which is important to achieve good HW utilization / makespans (explain!).
    \end{itemize}

    %%% MOTIVATION %%%
    \begin{itemize}
      \item Heterogeneous means: different CPU speeds, different mem sizes
      \item With different mem sizes: more difficult to adhere to mem constraints
      \item Adhering to memory constraints is very important to avoid execution failures.
      \item In this paper, we formulate the problem that takes memories into consideration (using (nearly the) model from ICPP paper)
      \item HEFT (see book chapter) is one of the most popular heuristics (cite a review).
      \item However, existing HEFT variations do not take memory sizes into consideration (\skug{check in related work if true!}).
        Note: 2 papers that deal with memory sizes, but model is very different!
      \item Many scheduling strategies assume that task running times provided to them are accurate. This is not really the case
        in practice. Thus, one needs to adapt the schedule when major deviations occur (which is the case in practice).
        List-based schedulers such as HEFT are not designed for adaptation and would compute a completely schedule from scratch.
    \end{itemize}

@@

    For the size-increased workflows, the graph is produced by the WFGen generator, based on a {\em model workflow} and
    the desired number of tasks.
    We used the real-world workflows as models, except for bacass that lead to errors in the generator.
%
    As number of tasks, we use: 200, \numprint{1000}, \numprint{2000}, \numprint{4000}, \numprint{8000}, \numprint{10000},
    \numprint{15000}, \numprint{18000}, \numprint{20000}, \numprint{25000}, \numprint{30000}.
    We divide the workflows into four groups by size: tiny ones with up to \numprint{200} tasks, small ones with \numprint{1000} to \numprint{8000} tasks,
    middle ones with \numprint{10000} to \numprint{18000} tasks, and big ones with \numprint{20000} to \numprint{30000} tasks.
